Enhancing Forecast Reconciliation: A Study of Alternative Covariance Estimators

### 2025-07-30 literature/paper_draft.qmd
write on results empirical findings

Regarding reconciliation strategies, we consider OLS, mint_shr (MinT with Shrinkage estimator), and mint_n (MinT with NOVELIST estimator). Note that the number of series is larger than the number of observations (560 compared to 96), hence the sample covariance matrix is not positive definite and will not be considered

```{r}
visnights_full <- readRDS("literature/lib/visnights_full.rds")
```

```{r}
#| label: fig-STL-tourism
#| fig-cap: "Monthly domestic overnight tourism nights in Australia by state, with STL decomposition to extract trend component"
#| fig.width: 8
#| fig.height: 6
#| out.width: "100%"
#| fig.align: "center"
visnights_full %>% 
  filter(
    is_aggregated(Purpose) & is_aggregated(Zone) & is_aggregated(Region),
    !is_aggregated(State)
  ) %>% 
  model(
    STL(Nights)
  ) %>% 
  components() %>% 
  pivot_longer(
    cols = c(Nights, trend, season_year, remainder, season_adjust),
    names_to = "component",
    values_to = "value"
  ) %>%
  filter(
    component == c("Nights", "trend"),
    year(Month) >= 2000
  ) %>%
  as_tibble() %>%
  mutate(component = recode(component,                     # give them nicer names
                            Nights = "Observed Nights",
                            trend  = "STL Decomposed Trend")) %>% 
  ggplot(aes(Month, value, color = as.character(State))) +
    geom_line() +
    facet_wrap(~ component, ncol=1, scales = "free_y") +
    labs(
      x = "Month",
      y = "Visitor Nights (in thousands)",
      color = "State"
    ) +
    theme_bw()
```

Additionally, we notice a structural change in the tourism data after 2016, which is characterised by a slight upward trend in demand, as illustrated in @fig-STL-tourism. The trend component is extracted using STL decomposition [@??] on the monthly domestic overnight tourism nights in Australia by state. This trend only happened in New South Wales, Victoria, Queensland, and Western Australia, which is likely due to the increasing popularity of tourism in these places, as well as the impact of various factors such as economic growth, population growth, and changes in consumer preferences. Our empirical analysis show that the base forecasts produced by the ARIMA models are not able to capture this trend, leading to even poorer performance of reconciliation methods. To account for this, we will also evaluate the performance of reconciliation methods on the data set excluding the period after 2016, which is from January 1998 to December 2016 (the last training window ends on December 2015).

@@

```{r}
#| label: fig-tourism-results
#| fig-cap: "Relative improvement of the MSE of reconciled forecasts over the base forecasts for the Australian domestic tourism flows"
#| fig.width: 8
#| fig.height: 10
#| out.width: "100%"

@@

```{r}
#| label: fig-tourism-results-ex1026
#| fig-cap: "Relative improvement of the MSE of reconciled forecasts over the base forecasts for the Australian domestic tourism flows, excluding the period after 2016"
#| fig.width: 8
#| fig.height: 10
#| out.width: "100%"

@@

>>>>

@@

```{r fig tourism results}
#| label: fig-tourism-results
#| fig-cap: "Relative improvement of the MSE of reconciled forecasts over the base forecasts for the Australian domestic tourism flows"
#| fig.width: 8
#| fig.height: 10
#| out.width: "100%"

@@

```{r fig STL tourism}
#| label: fig-STL-tourism
#| fig-cap: "Monthly domestic overnight tourism nights in Australia by state, with STL decomposition to extract trend component"
#| fig.width: 8
#| fig.height: 6
#| out.width: "100%"
#| fig.align: "center"

visnights_full <- readRDS("literature/lib/visnights_full.rds")

visnights_full %>% 
  filter(
    is_aggregated(Purpose) & is_aggregated(Zone) & is_aggregated(Region),
    !is_aggregated(State)
  ) %>% 
  model(
    STL(Nights)
  ) %>% 
  components() %>% 
  pivot_longer(
    cols = c(Nights, trend, season_year, remainder, season_adjust),
    names_to = "component",
    values_to = "value"
  ) %>%
  filter(
    component == c("Nights", "trend"),
    year(Month) >= 2000
  ) %>%
  as_tibble() %>%
  mutate(component = recode(component,                     # give them nicer names
                            Nights = "Observed Nights",
                            trend  = "STL Decomposed Trend")) %>% 
  ggplot(aes(Month, value, color = as.character(State))) +
    geom_line() +
    facet_wrap(~ component, ncol=1, scales = "free_y") +
    labs(
      x = "Month",
      y = "Visitor Nights (in thousands)",
      color = "State"
    ) +
    theme_bw()
```

Regarding reconciliation strategies, we consider OLS, mint_shr (MinT with Shrinkage estimator), and mint_n (MinT with NOVELIST estimator). Note that the number of series is larger than the number of observations (560 compared to 96), hence the sample covariance matrix is not positive definite and will not be considered.

The results are presented in @fig-tourism-results, which shows the relative improvement of the MSE of reconciled forecasts over the base forecasts for the Australian domestic tourism flows. The results are grouped by levels of aggregation. We can clearly see that MinT with either Shrinkage (mint_shr) or NOVELIST estimator (mint_n) improve the point forecast accuracy over the base ARIMA models for middle to lower aggregation levels. We hardly differentiate the point accuracy performance between mint_shr and mint_n in these level, except at the most disaggregated, where mint_shr has slightly larger improvement.

However, surprisingly, MinT performs worse over OLS at higher aggregation level, and especially worse than the base models at country-wise. This contradicts with the empirical results from @Wickramasuriya2019-xq and others. Further inspection draws our attention to a structural change in the tourism data after 2016, which is characterised by a slight upward trend in demand, as illustrated in @fig-STL-tourism. The trend component is extracted using STL decomposition [@??] on the monthly domestic overnight tourism nights in Australia by state. This trend only happened in New South Wales, Victoria, Queensland, and Western Australia, which is likely due to the increasing popularity of tourism in these places, as well as the impact of various factors such as economic growth, population growth, and changes in consumer preferences.

```{r}
#| label: fig-tourism-results-ex2016
#| fig-cap: "Relative improvement of the MSE of reconciled forecasts over the base forecasts for the Australian domestic tourism flows, excluding the period after 2016"
#| fig.width: 8
#| fig.height: 10
#| out.width: "100%"

@@

Our empirical analysis show that the base forecasts produced by the ARIMA models are not able to capture this trend, leading to even poorer performance of reconciliation methods. To account for this, we will also evaluate the performance of reconciliation methods on the data set excluding the period after the year 2016 (the last training window ends on December 2015), in which the results are shown in @fig-tourism-results-ex2016.

In this case, we can clearly observe that both MinT methods return the most accurate forecasts. At higher aggregation levels (Australia, State, and Australia by Purposes levels), we no longer see the patterns as in @fig-tourism-results. In contrast, MinT performs drastically better than the base models. Additionally, the higher the aggregation level, the more accurate mint_n is over mint_shr. This is an advantage of NOVELIST estimator. At higher levels most series are combinations of many bottom cells, the base forecast error correlations are strong and genuinely useful. NOVELIST keeps the large cross-series correlations at those higher levels, while its thresholding feature minimises the effects of weak, noisy links.

The Australian domestic tourism data shred lights on the potentials of NOVELIST estimator, having results that we did not produce in our previous simulation settings. Further ahead, we aim to incorporate the structure of the tourism flows into our data generating process settings, and further explore the cases where mint_n can take advantage of the features that mint_shr can not. Nevertheless, improving the forecasts of Australian tourism demand after the structural change occured is another question we should keep in mind.
